Borel regularity for ODEs and Thimble Integrals

### 2023-11-08 exp-resurgence.tex
Appendix B moved to draf2.tex part of the content of Appedix B is now in thimble proj formula for Airy.

We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. 
For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$, \textcolor{orange}{oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$}.

\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{The preimage of a ray departing from the critical value and going to infinity.}
    \label{fig:thimble_vs_rays}
\end{figure}
Then, our main result for thimble integrals is proving that $1$- dimensional thimble integrals are indeed Borel regular:
\begin{theorem}[see Theorem \ref{thm:maxim}]
    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$. Then:
\begin{enumerate}
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
\begin{multline}\label{eqn:formula}
\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[Be careful about the orientation of $\Lambda_j$.]}
\end{enumerate}
\end{theorem}

@@

For every $j=1,...,d$, let $\Omega_j\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha_j$. We also assume:
\begin{itemize}
\item The set $\Omega_j$ is star-shaped around $\zeta = \alpha_j$. In other words, for any $a \in \Omega_j$, a straight path from $\zeta = \alpha_j$ to $a$ stays in $\Omega_j$. Since $\Omega_j$ doesn't contain $\zeta = \alpha_j$, we'll always leave that starting point out of the path.
\item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}.
\end{itemize}

\begin{figure}
\center
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha_j$};
\node at (1.7,1.8) {$\bullet$};
\node[below] at (1.7,1.8) {$\zeta=\alpha_k$};
\node at (1.25,-1.85) {$\bullet$};
\node at (-0.58,1.85) {$\bullet$};
\end{tikzpicture}
\caption{The domain $\Omega_j$}\label{Fig:domain}
\end{figure}
\subsubsection{Main results}
%As a consequence of Theorem 4 in {\tt reg-volterra} we get 
%
%\begin{theorem}\label{thm1-dim}
%In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
%\begin{equation}\label{P-hat_j}
%\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
%\end{equation}
%such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
%${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$.
%\end{theorem}

@@

\subsubsection{Main result}
\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\Phi}_{j}(z)\defeq e^{-z\alpha_j}(2\pi)^{1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$. Then:
\begin{enumerate}
\item\label{int:series-gevrey} The series $\tilde{\Phi}_j$ is $1$-Gevrey, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item\label{int:resum-valid} If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have
\begin{multline}\label{formula1}
\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta} {\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[Be careful about the orientation of $\Lambda_j$.]}
\end{enumerate}
\end{theorem}

@@

Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $\alpha_j$ with $\tfrac{1}{2} \tau^2 = f - f(\alpha_j)$. Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $\alpha_j$ and from $\alpha_j$ to the future, respectively. We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively. \textcolor{magenta}{[We should explicitly spell out and check the conditions that make this possible. I think we're implicitly orienting $\Lambda_j$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
that converges in some disk $|\tau| < \varepsilon$.

@@

\begin{figure}[ht]
    \centering
   \includegraphics[scale=0.3]{figures/thimble-n5.png}
    \caption{Integration contour $\Lambda_j$ for the Airy--Lucas function with $n=5$. The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=$. While the light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
    \label{fig:thimble_n_5}
\end{figure}

@@

In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (\S\ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (\S\ref{contour-argument-AL}). In both cases we find 
\begin{align*}
    v_1(\zeta)= i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
\end{align*}
which has a fractional power singularity at $\zeta=1$. In addition, notice that the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions. More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new germ of holomorphic function, which has a branch cut singularity at $\zeta=-1$. Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$: 
\begin{align*}
&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right)=\\
&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
&=2 i\cos(\pi m/n) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
&=2\cos(\pi m/n) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
&=2\cos(\pi m/n)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
\end{align*}
Hence, we deduce  
\begin{equation}\label{resurgent-relation-1}
    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1+i\varepsilon)=2i \cos(\pi m/n)  v_{-1}(\zeta)
\end{equation}
namely, that the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$. This is an instance of \textit{resurgent functions}, introduced by \'Ecalle in \cite{EcalleI,EcalleII,EcalleIII}\footnote{If the reader is interested in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i,Dorigoni,aniceto2019primer}.}. Although we’ll not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain. The same phenomena were described by Berry and Howls \cite{berry1991hyperasymptotics} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.

@@

It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pair of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and Figure \ref{fig:intersection_thimbles}. However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain. \textcolor{orange}{ I think we should argue we have the action of the permutation which leaves the base unchanged but gives a }

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.45]{figures/contour1-AL4--12.jpg}
    \includegraphics[scale=0.45]{figures/contour2-AL4--12.jpg}
    \includegraphics[scale=0.45]{figures/contour--AL4--12--inter.jpg}
    \includegraphics[scale=0.45]{figures/contour1-AL5--12.jpg}
    \includegraphics[scale=0.45]{figures/contour2-AL5--12.jpg}
    \includegraphics[scale=0.45]{figures/contour--AL5--12--inter.jpg}
    \caption{Graphically, we can describe the Stokes phenomenon by looking at the intersection points of \textit{dual pairs of thimbles}, which differ by a rotation of angle $\pi$. We choose $n=4$ and $n=5$. }
    \label{fig:intersection_thimbles}
\end{figure}

@@

\textcolor{magenta}{[The generalized Airy example is not completed and there are still some difficulties in the computations. In particular the thimble integral interpretation is missing Should we remove it?]}

In \cite{Reid} and \cite[Appendix]{drazin-reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation. They are defined as countour integral \cite[Section 9.13(ii)]{dlmf}

@@

Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
\begin{align*}
    u(\zeta)&=\cos\Big(\frac{1}{3}\arccos\zeta-\frac{2\pi k}{3}\Big) \quad k=0,1,2\\
    &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
\end{align*}
\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
\subsubsection{An eye on resurgence}\label{sec:eye-res-airy}
Resurgent functions have very special features: they are \textit{endlessly} analytically continuable away from the singularities, and by studying one germ we could typically reconstruct the others by looking at the behaviour near the singular points. A prototypical class of resurgent functions is the so-called simple resurgent functions, namely analytic function $\hat{\phi}$ with singularities $\omega$ such that 
\begin{align*}
    \hat{\phi}(\zeta-\omega)=\frac{S_\omega}{2\pi i} \log(\zeta) \series{\phi}_\omega(\zeta) + \text{ hol. funct.}
\end{align*}
where $S_\omega$ is a constant, typically assumed to be integral (in a suitable normalization) and called the Stokes constant of the singularity $\omega$. The goal of resurgence is to investigate the location of the singularities together with their Stokes constants and the corresponding germs $\series{\phi}_\omega$.  
The main idea of resurgence is that studying the analytic continuation of $\tilde{\phi}_\omega$  
Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in equation \eqref{formula1} are resurgent functions. Their resurgent structure can be easily reconstructed: if $\nu$ is holomorphic, then $\hat{\phi}_j$ is singular at $\zeta_j=\alpha_k$ for $k\neq j$. Hence the set of singularities is given by the critical values of $f$.  Since $f$ has finitely many critical values, we can

>>>>

We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform. The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate. 
For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$. These are well-defined as long as $\Gamma_j$ misses the critical values of $f$. The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$. The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$. However, this only seems to be possible when $X$ is 1-dimensional.}}

\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{The preimage of a ray departing from the critical value and going to infinity.}
    \label{fig:thimble_vs_rays}
\end{figure}
Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
\begin{theorem}[see Theorem \ref{thm:maxim}]
    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$. Then:
\begin{enumerate}
\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
\begin{multline}\label{eqn:formula}
\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{enumerate}
\end{theorem}

@@

For every $j=1,...,d$, let $\Omega_j\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha_j$. We also assume:
\begin{itemize}
\item The set $\Omega_j$ is star-shaped around $\zeta = \alpha_j$. In other words, for any $a \in \Omega_j$, a straight path from $\zeta = \alpha_j$ to $a$ stays in $\Omega_j$. Since $\Omega_j$ doesn't contain $\zeta = \alpha_j$, we'll always leave that starting point out of the path.
\item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}. \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_j$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure). Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
\end{itemize}

\begin{figure}
\center
\begin{tikzpicture}
\newcommand{\spill}{4}
\fill[violet!20, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha_j$};
\node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\alpha_k$};
\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
  \fill \p circle (0.7mm);
}
\end{tikzpicture}
\caption{The domain $\Omega_j$}\label{Fig:domain}
\end{figure}
\subsubsection{Main results}
%As a consequence of Theorem 4 in {\tt reg-volterra} we get 
%
%\begin{theorem}\label{thm1-dim}
%In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
%\begin{equation}\label{P-hat_j}
%\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
%\end{equation}
%such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
%${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$.
%\end{theorem}

@@

\subsubsection{Main result}
\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\Phi}_{j}(z)\defeq e^{-z\alpha_j}(2\pi)^{1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$. Then:
\begin{enumerate}
\item\label{int:series-gevrey} The series $\tilde{\Phi}_j$ is $1$-Gevrey, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
\item\label{int:resum-valid} If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have
\begin{multline}\label{formula1}
\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta} {\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
\end{multline}
where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$. Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$. \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
\end{enumerate}
\end{theorem}

@@

Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a_j$ with $\tfrac{1}{2} \tau^2 = f - f(a_j)$. Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $a_j$ and from $a_j$ to the future, respectively. We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively. \textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
that converges in some disk $|\tau| < \varepsilon$.

@@

\begin{figure}[ht]
    \centering
   \includegraphics[scale=0.3]{figures/thimble-n5.png}
    \caption{Integration contour $\Lambda_j$ for the Airy--Lucas function with $n=5$. The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=???$. While the light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
    \label{fig:thimble_n_5}
\end{figure}

@@

In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}). In both cases we find 
\begin{align*}
    v_1(\zeta)= i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
\end{align*}
which has a fractional power singularity at $\zeta=1$. In addition, the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions. More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new holomorphic function (analytic continuation of a new germ at the origin), which has a branch cut singularity at $\zeta=-1$. Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$: 
\begin{align*}
&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right)=\\
&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
&=2 i\cos(\pi m/n) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
&=2\cos(\pi m/n) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
&=2\cos(\pi m/n)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
\end{align*}
Hence, we deduce  
\begin{equation}\label{resurgent-relation-1}
    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1+i\varepsilon)=2i \cos(\pi m/n)  v_{-1}(\zeta)
\end{equation}
namely, that the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$. This is an instance of \textit{resurgent functions}, introduced by \'Ecalle in \cite{EcalleI,EcalleII,EcalleIII}\footnote{If the reader is interested in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i,Dorigoni,aniceto2019primer}.}. Although we’ll not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain. The same phenomena were described by Berry and Howls \cite{berry1991hyperasymptotics} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.

@@

It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and Section \ref{sec:Picard-Lefschetz}. However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain. \textcolor{orange}{ I think we should argue we have the action of the permutation which leaves the base unchanged but gives a }

@@

\textcolor{magenta}{[The generalized Airy example is not completed and there are still some difficulties in the computations. In particular, the thimble integral interpretation is missing Should we remove it?]}

In \cite{Reid} and \cite[Appendix]{drazin-reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation. They are defined as contour integral \cite[Section 9.13(ii)]{dlmf}

@@

Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
\begin{align*}
    u(\zeta)&=\cos\Big(\frac{1}{3}\arccos\zeta-\frac{2\pi k}{3}\Big) \quad k=0,1,2\\
    &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
\end{align*}
\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
The thimble $\Lambda_1$ \textcolor{red}{is/can be} parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
\begin{align*}
\int_{\Lambda_1(\zeta)} \nu & = \int_{\Lambda_1(\zeta)} du \\
& = u \Big|_{\operatorname{start} \Lambda_1(\zeta)}^{\operatorname{end} \Lambda_1(\zeta)}.
\end{align*}
Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\Lambda_1(\zeta)$ are characterized by
\begin{align*}
u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
\zeta & = \cosh(3\theta),
\end{align*}
so
\begin{align*}
\int_{\Lambda_1(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
& = -i\sqrt{3}\,\sinh(\theta).
\end{align*}
Let $\xi = \tfrac{1}{2}(1 - \zeta)$, and notice that $\xi = -\sinh( \theta)^2$ at the start and end points. The identity~15.4.16 \cite{dlmf}
\[ \sinh(\theta) =  \sinh( \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\theta)^2\big) \]
then shows us that
\[ \frac{i}{\sqrt{3}} \int_{\Lambda_1(\zeta)} \nu = (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
